From textual to structured Web API Descriptions\\ \large Knowledge Discovery and Data Mining Seminar 2017

### 2017-08-29 Paper/Paper_KDD.tex
Algorithmen update

\begin{algorithm}[H]
 \caption{Algorithm 1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
\FOR {$\forall s_1 \in API$}
\FOR {$\forall s_2 \in API$} 
\STATE \begin{equation*}{Sim}_{con}\left(s_1,s_2\right)=\frac{\sum_{\epsilon\ {con}_{s1}}\sum_{w_j\epsilon\ {con}_{s2}}{sim(w_i,\ w_j)}}{\left|{con}_{s1}\right|\times\left|{con}_{s2}\right|} \end{equation*}
\ENDFOR
\ENDFOR
 \STATE Accumulate the to a correlation matrix
% als inspiration ;)
 %\\ \textit{LOOP Process}
  %\FOR {$i = l-2$ to $0$}
  %\STATE statements..
  %\IF {($i \ne 0$)}
  %\STATE statement..
  %\ENDIF
  %\ENDFOR
 %\RETURN $P$
 \end{algorithmic}
 \end{algorithm}

\begin{table}
\begin{tabular}{lll}
\hline
tester & test \\
\end{tabular}
\end{table}

@@

\begin{algorithm}[H]
 \caption{Algorithm 3}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, \newline word-vectors of the APIs $W={w_1, w_1, ... w_n}$
 \ENSURE  k centres
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE Repeat \newline
\noindent\hspace*{5mm}%		    
			Assign each item $w_i$ to the cluster which has \newline 
\noindent\hspace*{5mm}%
			the closest cetroid;\newline
\noindent\hspace*{5mm}%
			Calculate new mean for each cluster;\newline
\newline
	Until convergence criteria is met.
 \end{algorithmic}
 \end{algorithm}

>>>>

\begin{algorithm}[H]
 \caption{Algorithm 1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
\FOR {$\forall s_1 \in API$}
\FOR {$\forall s_2 \in API$} 
\STATE \begin{equation*}{Sim}_{con}\left(s_1,s_2\right)=\frac{\sum_{\epsilon\ {con}_{s1}}\sum_{w_j\epsilon\ {con}_{s2}}{1-NGD(w_i,\ w_j)}}{\left|{con}_{s1}\right|\times\left|{con}_{s2}\right|} \end{equation*}
 \STATE Add ${Sim}_{con}\left(s_1,s_2\right)$ to the correlation matrix 
\ENDFOR
\ENDFOR
\RETURN correlation matrix

% als inspiration ;)
 %\\ \textit{LOOP Process}
  %\FOR {$i = l-2$ to $0$}
  %\STATE statements..
  %\IF {($i \ne 0$)}
  %\STATE statement..
  %\ENDIF
  %\ENDFOR
 %\RETURN $P$
 \end{algorithmic}
 \end{algorithm}

@@

\begin{algorithm}[H]
 \caption{Algorithm 3}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, \newline word-vectors of the APIs $W={w_1, w_1, ... w_n}$
 \ENSURE  k centres, affiliation of the APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE Repeat \newline
\noindent\hspace*{5mm}%		    
			Assign each item $w_i$ to the cluster which has \newline 
\noindent\hspace*{5mm}%
			the closest cetroid;\newline
\noindent\hspace*{5mm}%
			Calculate new mean for each cluster;\newline
	Until convergence criteria is met.
\RETURN centres, affiliation of the APIs
 \end{algorithmic}
 \end{algorithm}
